Lifting CDCL to Relational Domains

### 2016-10-15 domains.tex
meet irreducibles

\begin{definition}{(Complementable Meet Irreducible)} 
A meet irreducible $m\in A$ is called complementable iff $\exists
\bar{m} \in A: m\meet\bar{m}=\bot \wedge m\join\bar{m}=\top$.  
%A complementable meet irreducible $\bar{M}$ of an abstract lattice $A$ is the complement of a meet 
%irreducible $M \in A$ such that $\bar{M} \in A$ and the concretisation of $M$ 
%is the set complement of $\bar{M}$.  
%If every meet irreducible in $A$ is complementable, then $A$ is said to
%be have complementable meet irreducibles.
\end{definition}

@@

@@

\begin{definition}{(Meet Decomposition)} A meet decomposition of an abstract
element $a \in A$ is a set of meet irreducibles $M \subseteq A$ such that 
$\forall m_i \in M, \meet(m_i) = a$, where $max(i) = |M|$.
\end{definition}

>>>>

\begin{definition}{(Complementable Meet Irreducible)} 
A meet irreducible $m\in A$ is called \emph{complementable} iff $\exists
\bar{m} \in A: m\meet\bar{m}=\bot \wedge m\join\bar{m}=\top$.  
%A complementable meet irreducible $\bar{M}$ of an abstract lattice $A$ is the complement of a meet 
%irreducible $M \in A$ such that $\bar{M} \in A$ and the concretisation of $M$ 
%is the set complement of $\bar{M}$.  
%If every meet irreducible in $A$ is complementable, then $A$ is said to
%be have complementable meet irreducibles.
\end{definition}

@@

\begin{definition}{(Meet Decomposition)} A meet decomposition of an abstract
element $a \in A$ is a set of meet irreducibles $M \subseteq A$ such that 
$a=\bigscap_{m\in M} m$.
%$forall m_i \in M, \meet(m_i) = a$, where $max(i) = |M|$.
\end{definition}

@@
